
%%%%%%%%% BIOGRAPHICAL SKETCH -- 2 pages

\required{Lindley Anne Winslow}

{\bf Professional Preparation:} 
\newline \noindent
Postdoctoral Fellow in Physics, December 2008-July 2012, MIT
\newline \noindent
Ph.D. in Physics, December 2008, UC Berkeley
\newline \noindent
M.A. in Physics, December 2007, UC Berkeley
\newline \noindent
B.A. in Astrophysics and Physics, May 2001, UC Berkeley.
\newline\newline \noindent
{\bf Appointments:} 
\newline \noindent
Assistant Professor, July 2012-Present, UCLA
\newline\newline \noindent
{\bf Select  Publications:}
\newline\newline\noindent
{\it Related to this Proposal}
\newline\noindent
Double Chooz Collaboration, Y.~Abe {\it et al.}, ``Reactor electron antineutrino disappearance in the Double Chooz experiment,'' Phys.\ Rev.\ D {\bf 86}, 052008 (2012), arXiv:1207.6632 [hep-ex]. 
\newline\newline \noindent
IsoDAR Collaboration, A.~Bungau {\it et al.},``Proposal for an Electron Antineutrino Disappearance Search Using High-Rate Li-8 Production and Decay,'' Phys.\ Rev.\ Lett.\  {\bf 109}, 141802 (2012),  arXiv:1205.4419 [hep-ex].
\newline\newline \noindent
L.~Winslow and R.~Simpson, ``Characterizing Quantum-Dot-Doped Liquid Scintillator for Applications to Neutrino Detectors,'' JINST {\bf 7}, P07010 (2012), arXiv:1202.4733 [physics.ins-det].
\newline\newline \noindent
KamLAND Collaboration, S.~Abe {\it et al.}, ``Production of Radioactive Isotopes through Cosmic Muon Spallation in KamLAND,'' Phys.\ Rev.\ C {\bf 81}, 025807 (2010), arXiv:0907.0066 [hep-ex].
\newline\newline \noindent
KamLAND Collaboration, B.~E.~Berger {\it et al.}, ``The KamLAND Full-Volume Calibration System,'' JINST {\bf 4}, P04017 (2009), arXiv:0903.0441 [physics.ins-det].
\newline\newline \noindent
{\it Other Publications}
\newline \noindent
Double Chooz Collaboration, Y.~Abe {\it et al.}, ``Direct Measurement of Backgrounds using Reactor-Off Data in Double Chooz,'' (2012), arXiv:1210.3748 [hep-ex].
\newline\newline \noindent
C.~L.~Jones, A.~Bernstein, J.~M.~Conrad, Z.~Djurcic, M.~Fallot, L.~Giot, G.~Keefer and A.~Onillon, ``Reactor Simulation for Antineutrino Experiments using DRAGON and MURE,'' Phys.\ Rev.\ D {\bf 86}, 012001 (2012), arXiv:1109.5379 [nucl-ex].
\newline\newline\noindent
J. Lopez, K. Terao, J.M. Conrad, D. Dujmic, L. Winslow, ``A prototype detector for directional measurement of the cosmogenic neutron flux,"  NIM A {\bf 673},  22-31 (2012).
\newline\noindent
http://dx.doi.org/10.1016/j.nima.2012.01.021.
\newline\newline \noindent
Double Chooz Collaboration, Y.~Abe {\it et al.}, ``Indication for the disappearance of reactor electron antineutrinos in the Double Chooz experiment,'' Phys.\ Rev.\ Lett.\  {\bf 108}, 131801 (2012), arXiv:1112.6353 [hep-ex].
\newline\newline \noindent
KamLAND Collaboration, S.~Abe {\it et al.}, ``Measurement of the 8B Solar Neutrino Flux with the KamLAND Liquid Scintillator Detector,'' Phys.\ Rev.\ C {\bf 84}, 035804 (2011), arXiv:1106.0861 [hep-ex].
\newline\newline \noindent
{\bf Synergistic Activities:}
\newline \noindent
Graduate Student Seminar: The Neutrino (Fall 2012)
\newline \noindent
http://http://nucla.physics.ucla.edu/node/6
\newline\newline \noindent
Talk Science! - A NSF-funded Inquiry Project (July 2011)
\newline \noindent
Participated in a video on the particle model of gases for middle school students.
\newline\newline \noindent
I $\heartsuit$ Neutrinos  (July 2011)
\newline \noindent
Aided MIT visiting artist Jennifer West with a mixed media film project.
\newline\newline \noindent
Physics for the 21st Century -Annenberg Foundation Project (October 2009 - July 2010)
\newline \noindent
Online course including interactive demonstration of neutrino oscillations.
\newline\newline \noindent
MIT Summer Research Program (Summer 2009-2011)
\newline \noindent
Research mentor for undergraduate summer students.
\newline\newline \noindent
{\bf  Collaborations:}
\newline \noindent
Graduate Advisor: Stuart J. Freedman, UC Berkeley
\newline \noindent
Postdoctoral Sponsor: Janet M. Conrad, MIT
\newline \noindent
Current Collaborators:
\newline \noindent
CUORE, Double Chooz, DAEdALUS/IsoDAR and KamLAND/KamLAND-Zen
% Your Bio should be divided into the following sections
% (a) Professional Preparation (education):
% Undergrad, Major, Year
% Graduate, Major, Year
% Postdoc, Area, Years-Inclusive
% (b) Appointments:  most recent first.
% (c) Publications:  5 related to the proposal, and 5 "Other Significant Publications"
% (d) Synergistic Activities (math-enhancing activities that were not
% part of your main job description, like editorial boards and
% conference organizing - any Math-related volunteer work.
% these are often similar to Broader Impacts

% (e) Collaborators & Other Affiliations: (use the following sections)
% list in alphabetical order, and include current affiliations parenthetically
% Collaborators and Co-editors: past 48 months.  If none, write "none"
% Graduate Advisors and Postdoctoral sponsors: (your own, no matter how long ago)
% Thesis advisor and postgraduate scholar-sponsor:  those you have advised
% in the past 5 years.  
% Total number of graduate students advised: X (all time)
% Total number of postdoctoral scholars sponsored: Y (all time)


